---
title: "librely Documentation"
author: "Alex Hope, Bonnie Zhang, Aaron Quinton"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{librely Documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

librely: Meta analysis of R scripts
===================================

The [librely](https://github.com/UBC-MDS/LibRely-R-) package is designed to provide a meta analysis of R scripts to aid in the workflow for a data science or software development project. The functionalities in this package interpret scripts to compile library/module dependencies, document specific functions imported in the script and measure the length of the script by the number of lines and characters.  

The user can use LibRely to better understand the packages used in a script authored by someone else. Alternatively, a user can take advantage of the functionalities when preparing the ReadMe documentation in their project. The following functions are included in the LibRely package.  



`librely` functions
-----------------------
To conduct the meta analysis of your R script the package includes the following three functions:

* `lib_search()` : This function finds the packages used in the R script and returns a vector of their names.

* `lib_count()` : This function finds the functions used throughout the R script and which package they belonged to. It returns a dataframe of this information.

* `lib_lines()` : This function gives a sense of the size of the script by returning a list of the number of lines and characters in the script.



Demonstration
-----------------------

```{r}
library(librely)

lib_search("../tests/testthat/file/script_for_test1.R")

lib_count("../tests/testthat/file/script_for_test1.R")

lib_lines("../tests/testthat/file/script_for_test1.R")

```
